ITS\_LIVE: A Cloud-Native Approach to Monitoring Glaciers from Space

### 2023-10-29 paper.tex
moving things around

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, boxrule=0pt, interior hidden, breakable, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

>>>>

\begin{keyword}
    glaciology \sep climate change \sep big data \sep 
    cloud computing
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi
